\LARGE \bf Learning Depth-Sensitive Conditional Random Fields for Semantic Segmentation of RGB-D Images

### 2013-09-13 paper.tex
Fix table caption
git-svn-id: https://svn.ais.uni-bonn.de/svn/staff/publications/icra_2014_mueller_nyu@4373 b2511e17-9ac0-488b-bc21-1d6d82e5baa2

\begin{table*}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
                        & ground        &  structure    & furniture     & props         & class average   & pixel average\\
\cmidrule(r){1-7}

@@

\bottomrule
\end{tabularx}
    \caption{Quantitative comparison of the proposed method with the
literature. The best value in each column is printed in bold. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.\tablabel{results}}
\end{table*}

>>>>

\begin{table*}[t]
    \caption{Quantitative comparison of the proposed method with the
    literature.\tablabel{results}}
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
                        & ground        &  structure    & furniture     & props         & class average   & pixel average\\
\cmidrule(r){1-7}

@@

\bottomrule
\end{tabularx}
\quad\\The best value in each column is printed in bold. The upper part of
the table shows contributions by different parts of our pipeline. RF stands for random forest prediction, RF + SP for aggregated
random forests prediction within superpixels, RF + SP + SVM for an SVM trained on the unary potentials, and RF + SP + CRF is
our proposed pipeline. We optimized our approach for class average
accuracy.
\end{table*}
